Geometrization of characters of tori over non-archimedean local fields

### 2013-08-15 shanghai.tex
Commit for our meeting.

In principle, something similar is possible in the more general 
context of this paper, where $G$ is a smooth group scheme 
locally of finite type over $\Fq$, to which we now return. 
Every quasicharacter sheaf $(\gcs{L},\mu,\phi)$ on $G$ 
determines a Weil sheaf $(\gcs{L},\phi)$ on $G$. 
So, if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$, then this choice can be used to convert 
the Weil sheaf $(\gcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
It proved cumbersome, however, to manage various 
choices of families of base points and track the action 
of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of 
Weil groups, and difficult to identify the relevant quotient of this group. Viewed in this light, Definition~\ref{def:QC} seemed comparatively simple.

>>>>

In principle, something similar is possible in the more general 
context of this paper, where $G$ is a smooth group scheme 
locally of finite type over $\Fq$, to which we now return. 
In this generality, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
see the end of Section~\ref{sec:snake}.
Nevertheless, every quasicharacter sheaf $(\gcs{L},\mu,\phi)$ on $G$ 
determines a Weil sheaf $(\gcs{L},\phi)$ on $G$. 
So, if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$, then this choice can be used to convert 
the Weil sheaf $(\gcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
It proved cumbersome, however, to manage various 
choices of families of base points and track the action 
of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of 
Weil groups, and difficult to identify the relevant quotient of this group. Viewed in this light, Definition~\ref{def:QC} seemed comparatively simple.
